\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{lmodern}
\usepackage[T1]{fontenc}

\title{Two-Type Example: Capacity Sorting in the $\beta=0$ Regime}
\date{}

\begin{document}
\maketitle

Consider a two-type version of the within-category problem, with a low type $\theta_L$, a high type $\theta_H>\theta_L$, and population shares $p\in(0,1)$ and $1-p$. Let the social weights be $\lambda_L$ and $\lambda_H$, and define the average weight
\[
\tilde{\lambda}=p\lambda_L+(1-p)\lambda_H.
\]
We focus on the regime $\beta=0$, so that the effective weights coincide with $\Gamma_L$ and $\Gamma_H$.

\section{Two-type objects}

The two-type analogue of the revenue-productivity term is
\[
J_L=\theta_L-\frac{1-p}{p}\left(\theta_H-\theta_L\right),
\qquad
J_H=\theta_H.
\]
The corresponding effective welfare weights are
\[
\Gamma_L=\tilde{\lambda}J_L+\Lambda_L,
\qquad
\Gamma_H=\tilde{\lambda}J_H,
\]
with
\[
\Lambda_L=\frac{1-p}{p}\left(\theta_H-\theta_L\right)\lambda_H,
\qquad
\Lambda_H=0.
\]
Equivalently,
\[
\Gamma_H=\tilde{\lambda}\,\theta_H,
\]

and
\[
\Gamma_L
=
\tilde{\lambda}\left[\theta_L-\frac{1-p}{p}\left(\theta_H-\theta_L\right)\right]
+
\frac{1-p}{p}\left(\theta_H-\theta_L\right)\lambda_H.
\]
A useful alternative expression is
\[
\Gamma_L
=
\tilde{\lambda}\,\theta_L
+
\frac{\theta_H-\theta_L}{p}\left(\lambda_H-\tilde{\lambda}\right).
\]

\section{Allocation and capacity expansion when $\beta=0$}

Let $q_L$ and $q_H$ denote the quantities assigned to the low and high type in a binding state. The first-order conditions are
\[
\Gamma_L\,u(q_L)=\varepsilon,
\qquad
\Gamma_H\,u(q_H)=\varepsilon,
\]
where $u=U_q$ is marginal utility and $\varepsilon$ is the scarcity rent. The capacity constraint is
\[
pq_L+(1-p)q_H=k.
\]

Differentiating with respect to $k$ gives
\[
\Gamma_Lu_q(q_L)\frac{dq_L}{dk}=\frac{d\varepsilon}{dk},
\qquad
\Gamma_Hu_q(q_H)\frac{dq_H}{dk}=\frac{d\varepsilon}{dk},
\qquad
p\frac{dq_L}{dk}+(1-p)\frac{dq_H}{dk}=1.
\]
Therefore,
\[
\frac{dq_L}{dk}
=
\frac{\Gamma_Hu_q(q_H)}{(1-p)\Gamma_Lu_q(q_L)+p\Gamma_Hu_q(q_H)},
\qquad
\frac{dq_H}{dk}
=
\frac{\Gamma_Lu_q(q_L)}{(1-p)\Gamma_Lu_q(q_L)+p\Gamma_Hu_q(q_H)}.
\]

Define
\[
R_{dq}:=\frac{dq_H/dk}{dq_L/dk}.
\]
Then
\[
R_{dq}=\frac{w_H}{w_L},
\qquad
w_L:=-\frac{1}{\Gamma_Lu_q(q_L)},
\qquad
w_H:=-\frac{1}{\Gamma_Hu_q(q_H)}.
\]
Using the first-order conditions,
\[
\frac{\Gamma_L}{\Gamma_H}=\frac{u(q_H)}{u(q_L)},
\]
so
\[
R_{dq}=\frac{u(q_H)}{u(q_L)}\frac{u_q(q_L)}{u_q(q_H)}.
\]
If we define the curvature object
\[
R_q(q):=-\frac{u(q)}{u_q(q)},
\]
then
\[
R_{dq}=\frac{R_q(q_H)}{R_q(q_L)}.
\]
Thus, outside the CARA case, a marginal capacity increase need not be split one-for-one across types; the split is governed by the ratio of the curvature terms.

\section{The capacity-sorting object}

The discrete analogue of the revenue-productivity term is
\[
EUJ=pJ_LU(q_L)+(1-p)J_HU(q_H).
\]
Replacing $J_L$ and $J_H$ yields
\[
EUJ
=
\left[p\theta_L-(1-p)\left(\theta_H-\theta_L\right)\right]U(q_L)
+
(1-p)\theta_HU(q_H).
\]
Differentiating with respect to $k$ gives
\[
\frac{\partial EUJ}{\partial k}
=
\left[p\theta_L-(1-p)\left(\theta_H-\theta_L\right)\right]u(q_L)\frac{dq_L}{dk}
+
(1-p)\theta_Hu(q_H)\frac{dq_H}{dk}.
\]
Factorizing by $dq_L/dk$ and using $R_{dq}=\left(dq_H/dk\right)/\left(dq_L/dk\right)$,
\[
\frac{\partial EUJ}{\partial k}
=
\frac{dq_L}{dk}
\left\{
\theta_Lu(q_L)
-
(1-p)\theta_H\left[u(q_L)-R_{dq}u(q_H)\right]
\right\}.
\]
Replacing marginal utility by the first-order conditions and factorizing by $\varepsilon$ gives
\[
\frac{\partial EUJ}{\partial k}
=
\frac{dq_L}{dk}\,\varepsilon
\left[
\frac{\theta_L}{\Gamma_L}
-
(1-p)\theta_H
\left(
\frac{1}{\Gamma_L}
-
\frac{R_{dq}}{\Gamma_H}
\right)
\right].
\]
Finally, using
\[
R_{dq}=\frac{R_q(q_H)}{R_q(q_L)},
\]
one obtains
\[
\frac{\partial EUJ}{\partial k}
=
\frac{dq_L}{dk}\,\varepsilon
\left[
\frac{\theta_L}{\Gamma_L}
-
(1-p)\theta_H
\left(
\frac{1}{\Gamma_L}
-
\frac{1}{\Gamma_H}\frac{R_q(q_H)}{R_q(q_L)}
\right)
\right].
\]
This is the key equation for the two-type example. It isolates three forces:
\begin{enumerate}
    \item the direct low-type contribution $\theta_L/\Gamma_L$;
    \item the standard high-type rent-pressure term $(1-p)\theta_H$;
    \item the peak-load allocation margin, through the curvature ratio $R_q(q_H)/R_q(q_L)$.
\end{enumerate}

\section{CARA benchmark}

Under CARA, $R_q(q)$ is constant, so
\[
\frac{R_q(q_H)}{R_q(q_L)}=1.
\]
Hence
\[
\frac{dq_L}{dk}=1,
\qquad
\frac{dq_H}{dk}=1,
\]
and the previous expression simplifies to
\[
\frac{\partial EUJ}{\partial k}
=
\varepsilon
\left[
\frac{\theta_L}{\Gamma_L}
-
(1-p)\theta_H\left(\frac{1}{\Gamma_L}-\frac{1}{\Gamma_H}\right)
\right].
\]
Setting this equal to zero yields
\[
\theta_L\Gamma_H=(1-p)\theta_H\left(\Gamma_H-\Gamma_L\right).
\]
Using
\[
\Gamma_H=\tilde{\lambda}\,\theta_H,
\qquad
\Gamma_H-\Gamma_L=\lambda_L\left(\theta_H-\theta_L\right),
\]
the cutoff is
\[
\lambda_L^{\ast}
=
\frac{\theta_L\tilde{\lambda}}{(1-p)\left(\theta_H-\theta_L\right)}.
\]
Therefore,
\[
\frac{\partial EUJ}{\partial k}<0
\qquad\Longleftrightarrow\qquad
\lambda_L>\lambda_L^{\ast}.
\]
If one imposes
\[
\tilde{\lambda}=1,
\qquad
\theta_H=\theta_L+1,
\]
then
\[
\lambda_L^{\ast}=\frac{\theta_L}{1-p}.
\]

\section{Economic interpretation}

The two-type example makes the capacity-sorting tension transparent. The negative force does not come from redistribution itself, but from the fact that the low type may have weak or even negative revenue productivity through $J_L$. Redistribution keeps the low type in the allocation through a large effective weight $\Gamma_L$. A capacity expansion can therefore lower $EUJ$ when the planner puts enough weight on a type whose utility is difficult to finance under incentive compatibility.

The CARA cutoff makes this tension especially clear:
\[
\lambda_L^{\ast}
=
\frac{\theta_L\tilde{\lambda}}{(1-p)\left(\theta_H-\theta_L\right)}.
\]
A larger $\theta_L$ raises the cutoff, making it harder to obtain $\partial EUJ/\partial k<0$. Intuitively, when the low type becomes less revenue-destroying, a stronger redistributive tilt is needed for a capacity expansion to reduce the revenue-productivity term.

\section{High-type surplus under a capacity expansion.}

Consider the two-type case in the unconstrained regime, \(\beta=0\), with fixed budget \(I\).
The low-type and high-type surpluses are
\[
ECS_L = EUJ - I,
\qquad
ECS_H = ECS_L + \left(\theta_H-\theta_L\right)U(q_L).
\]
Hence
\[
\partial_k ECS_L = \partial_k EUJ,
\qquad
\partial_k ECS_H
=
\partial_k EUJ
+
\left(\theta_H-\theta_L\right)u(q_L)\,\partial_k q_L.
\]

Using
\[
\partial_k EUJ
=
\theta_L\,u(q_L)\,\partial_k q_L
-
(1-p)\theta_H
\left[
u(q_L)\,\partial_k q_L-u(q_H)\,\partial_k q_H
\right],
\]
we obtain
\begin{align*}
\partial_k ECS_H
&=
\theta_L\,u(q_L)\,\partial_k q_L
-
(1-p)\theta_H
\left[
u(q_L)\,\partial_k q_L-u(q_H)\,\partial_k q_H
\right]
+
\left(\theta_H-\theta_L\right)u(q_L)\,\partial_k q_L \\
&=
\theta_H\,u(q_L)\,\partial_k q_L
-
(1-p)\theta_H
\left[
u(q_L)\,\partial_k q_L-u(q_H)\,\partial_k q_H
\right] \\
&=
p\,\theta_H\,u(q_L)\,\partial_k q_L
+
(1-p)\theta_H\,u(q_H)\,\partial_k q_H.
\end{align*}

This decomposition yields a simple observation. For the low type, the sign of the marginal surplus effect is governed by \(\partial_k EUJ\), which reflects the familiar tension between the direct gain from a higher allocation and the induced informational-rent cost. By contrast, for the high type, this informational-rent cost is exactly offset by the additional rent created by the increase in the low-type allocation. As a result, the marginal effect on \(ECS_H\) reduces to a weighted gain in gross utility:
\[
\partial_k ECS_H
=
p\,\theta_H\,u(q_L)\,\partial_k q_L
+
(1-p)\theta_H\,u(q_H)\,\partial_k q_H.
\]
Thus, the positivity of \(\partial_k ECS_H\) does not rely on any monotonicity of the fixed part of the tariff. It follows instead from an exact compensation between the IC-rent effect embedded in \(\partial_k EUJ\) and the high type's rent gain through \(q_L\).




Consider the object
\[
R_{\theta,t}:=\frac{J_t}{\Gamma_t},
\qquad
\Gamma_t=\tilde\lambda J_t+\Lambda_t,
\]
under $\beta=0$.
This note summarizes when $R_\theta$ is automatically increasing across types, and when monotonicity becomes a genuine restriction in the three-type case.

\section{Two types $R_\theta$}

With two types $L<H$, one has
\[
J_H=\theta_H,
\qquad
\Gamma_H=\tilde\lambda\theta_H,
\qquad
\Gamma_L=\tilde\lambda J_L+\Lambda_L,
\]
with $\Lambda_L>0$. Therefore
\[
R_{\theta,H}-R_{\theta,L}
=
\frac{\theta_H}{\tilde\lambda\theta_H}-\frac{J_L}{\Gamma_L}
=
\frac{1}{\tilde\lambda}-\frac{J_L}{\Gamma_L}
=
\frac{\Gamma_L-\tilde\lambda J_L}{\tilde\lambda\Gamma_L}
=
\frac{\Lambda_L}{\tilde\lambda\Gamma_L}>0,
\]
whenever $\Gamma_L>0$.
Hence, in the two-type case, $R_\theta$ is automatically increasing in type:
\[
R_{\theta,H}>R_{\theta,L}.
\]

\section{Three types $R_\theta$}

Now consider three types $L<M<H$. The nontrivial comparison is between $L$ and $M$.
One has
\[
R_{\theta,M}\ge R_{\theta,L}
\quad\Longleftrightarrow\quad
\frac{J_M}{\Gamma_M}\ge \frac{J_L}{\Gamma_L}
\quad\Longleftrightarrow\quad
J_M\Gamma_L\ge J_L\Gamma_M.
\]
Using
\[
\Gamma_L=\tilde\lambda J_L+\Lambda_L,
\qquad
\Gamma_M=\tilde\lambda J_M+\Lambda_M,
\]
this becomes
\[
J_M\Lambda_L\ge J_L\Lambda_M.
\]
Thus, in the three-type case, monotonicity of $R_\theta$ is no longer automatic. It is governed by the primitive comparison
\[
\boxed{J_M\Lambda_L\ge J_L\Lambda_M.}
\]


\subsection{Equal probabilities}

Assume now
\[
p_L=p_M=p_H=\frac13.
\]
Then
\[
J_L=3\theta_L-2\theta_M,
\qquad
J_M=2\theta_M-\theta_H,
\qquad
J_H=\theta_H,
\]
and
\[
\Lambda_L=(\lambda_M+\lambda_H)(\theta_M-\theta_L),
\qquad
\Lambda_M=\lambda_H(\theta_H-\theta_M).
\]
Hence the nontrivial monotonicity condition becomes
\[
\boxed{
(2\theta_M-\theta_H)(\lambda_M+\lambda_H)(\theta_M-\theta_L)
\ge
(3\theta_L-2\theta_M)\lambda_H(\theta_H-\theta_M).
}
\]

\subsection{ Normalization $\theta_H=1$ and $\theta_M=\theta_L+d$}

Assume
\[
\theta_H=1,
\qquad
\theta_M=\theta_L+d,
\qquad
0<d<1-\theta_L.
\]
Then
\[
J_L=\theta_L-2d,
\qquad
J_M=2\theta_L+2d-1,
\]
and
\[
\Lambda_L=(\lambda_M+\lambda_H)d,
\qquad
\Lambda_M=\lambda_H(1-\theta_L-d).
\]
Therefore, monotonicity fails, that is,
\[
R_{\theta,M}<R_{\theta,L},
\]
if and only if
\[
\boxed{
(2\theta_L+2d-1)(\lambda_M+\lambda_H)d
<
(\theta_L-2d)\lambda_H(1-\theta_L-d).
}
\]

If moreover $J_M>0$, that is,
\[
2\theta_L+2d-1>0,
\]
one can isolate $\lambda_M$:
\[
\boxed{
\lambda_M
<
\lambda_H
\left[
\frac{(\theta_L-2d)(1-\theta_L-d)}{(2\theta_L+2d-1)d}-1
\right].
}
\]

Finally,
\[
J_L<J_M
\quad\Longleftrightarrow\quad
\theta_L-2d<2\theta_L+2d-1
\quad\Longleftrightarrow\quad
d>\frac{1-\theta_L}{4}.
\]
Thus the joint conditions
\[
J_L<J_M
\qquad\text{and}\qquad
R_{\theta,M}<R_{\theta,L}
\]
amount to
\[
\boxed{
d>\frac{1-\theta_L}{4}
\qquad\text{and}\qquad
(2\theta_L+2d-1)(\lambda_M+\lambda_H)d
<
(\theta_L-2d)\lambda_H(1-\theta_L-d).
}
\]

\subsection{ Special case $\theta_L=0$}

If, in addition,
\[
\theta_L=0,
\qquad
\theta_M=d,
\qquad
\theta_H=1,
\]
then
\[
J_L=-2d,
\qquad
J_M=2d-1,
\]
and the failure of monotonicity becomes
\[
(2d-1)(\lambda_M+\lambda_H)d
<
(-2d)\lambda_H(1-d),
\]
that is,
\[
\boxed{(2d-1)\lambda_M< -\lambda_H.}
\]
For nonnegative weights, this can only hold if
\[
d<\frac12,
\]
in which case the condition is equivalent to
\[
\boxed{\lambda_M>\frac{\lambda_H}{1-2d}.}
\]
Moreover,
\[
J_L<J_M
\quad\Longleftrightarrow\quad
-2d<2d-1
\quad\Longleftrightarrow\quad
d>\frac14.
\]
Hence, under $\theta_L=0$, the joint conditions
\[
J_L<J_M
\qquad\text{and}\qquad
R_{\theta,M}<R_{\theta,L}
\]
become
\[
\boxed{
\frac14<d<\frac12
\qquad\text{and}\qquad
\lambda_M>\frac{\lambda_H}{1-2d}.
}
\]

\subsection{Takeaway}

The two-type case is too rigid: $R_\theta$ is automatically increasing. In contrast, the three-type case is genuinely richer. The monotonicity of $R_\theta$ becomes a primitive restriction, and the parameterization with $\theta_M=\theta_L+d$ makes this especially transparent.

\paragraph{Two-type case: reallocation under a change in social preferences.}

Consider the two-type within-category problem in the regime \(\beta=0\). In any binding state,
\[
\Gamma_L u(q_L)=\varepsilon,
\qquad
\Gamma_H u(q_H)=\varepsilon,
\qquad
p q_L+(1-p)q_H = k,
\]
with
\[
\tilde\lambda = p\lambda_L + (1-p)\lambda_H,
\qquad
\Gamma_H = \tilde\lambda \theta_H,
\qquad
\Gamma_L = \tilde\lambda J_L + \Lambda_L,
\]
and
\[
\Lambda_L = \frac{1-p}{p}\left(\theta_H-\theta_L\right)\lambda_H.
\]

Now consider an arbitrary perturbation \(\left(d\lambda_L,d\lambda_H\right)\). Since
\[
d\tilde\lambda = p\,d\lambda_L + (1-p)\,d\lambda_H,
\]
we obtain
\[
d\Gamma_H = \theta_H\, d\tilde\lambda,
\]
and
\[
d\Gamma_L
=
J_L\, d\tilde\lambda + d\Lambda_L
=
J_L\, d\tilde\lambda
+
\frac{1-p}{p}\left(\theta_H-\theta_L\right)d\lambda_H.
\]

Define the proportional change in the effective weight by
\[
R_{\mathcal G,L} := \frac{d\Gamma_L}{\Gamma_L},
\qquad
R_{\mathcal G,H} := \frac{d\Gamma_H}{\Gamma_H}.
\]
In this two-type \(\beta=0\) case, \(\mathcal G_t=\Gamma_t\), so \(R_{\mathcal G,t}\) is simply the proportional change in \(\Gamma_t\).

Differentiating the two first-order conditions gives
\[
u(q_L)\,d\Gamma_L + \Gamma_L u_q(q_L)\,dq_L = d\varepsilon,
\]
\[
u(q_H)\,d\Gamma_H + \Gamma_H u_q(q_H)\,dq_H = d\varepsilon.
\]
Using the original first-order conditions,
\[
u(q_L)=\frac{\varepsilon}{\Gamma_L},
\qquad
u(q_H)=\frac{\varepsilon}{\Gamma_H},
\]
we can rewrite these expressions as
\[
\Gamma_L u_q(q_L)\,dq_L
=
d\varepsilon - \varepsilon \frac{d\Gamma_L}{\Gamma_L}
=
d\varepsilon - \varepsilon R_{\mathcal G,L},
\]
and
\[
\Gamma_H u_q(q_H)\,dq_H
=
d\varepsilon - \varepsilon \frac{d\Gamma_H}{\Gamma_H}
=
d\varepsilon - \varepsilon R_{\mathcal G,H}.
\]

Subtracting the second equation from the first yields
\[
\Gamma_L u_q(q_L)\,dq_L
-
\Gamma_H u_q(q_H)\,dq_H
=
\varepsilon\left(R_{\mathcal G,H}-R_{\mathcal G,L}\right).
\]

\[
\Gamma_L u_q(q_L)\,dq_L/\left(R_{\mathcal G,H}-R_{\mathcal G,L}\right)
-
\Gamma_H u_q(q_H)\,dq_H/\left(R_{\mathcal G,H}-R_{\mathcal G,L}\right)
=
\varepsilon.
\]

    Using feasibility,
    \[
    p\,dq_L + (1-p)\,dq_H = 0,
    \qquad\text{that is}\qquad
    dq_H = -\frac{p}{1-p}dq_L,
    \]
    we obtain
    \[
    \left[
    \Gamma_L u_q(q_L)
    +
    \frac{p}{1-p}\Gamma_H u_q(q_H)
    \right]dq_L
    =
    \varepsilon\left(R_{\mathcal G,H}-R_{\mathcal G,L}\right).
    \]
Since \(u_q<0\), the term in brackets is negative. Therefore,
\[
\operatorname{sign}(dq_L)
=
\operatorname{sign}\left(R_{\mathcal G,L}-R_{\mathcal G,H}\right),
\]
and, by feasibility,
\[
\operatorname{sign}(dq_H)
=
\operatorname{sign}\left(R_{\mathcal G,H}-R_{\mathcal G,L}\right).
\]

Hence, the allocation shifts toward the type whose effective weight experiences the larger proportional increase.

\medskip

We now specialize to a mean-preserving perturbation of social preferences. By definition,
\[
d\tilde\lambda
=
p\,d\lambda_L + (1-p)\,d\lambda_H
=
0,
\]
so that
\[
d\lambda_H = -\frac{p}{1-p}d\lambda_L.
\]
It follows that
\[
d\Gamma_H = \theta_H\,d\tilde\lambda = 0,
\]
while
\[
d\Gamma_L
=
J_L\,d\tilde\lambda
+
\frac{1-p}{p}\left(\theta_H-\theta_L\right)d\lambda_H
=
\frac{1-p}{p}\left(\theta_H-\theta_L\right)d\lambda_H
=
-\left(\theta_H-\theta_L\right)d\lambda_L.
\]
Therefore,
\[
R_{\mathcal G,H}=0,
\qquad
R_{\mathcal G,L}
=
\frac{d\Gamma_L}{\Gamma_L}
=
-\frac{\theta_H-\theta_L}{\Gamma_L}d\lambda_L.
\]

Substituting this into the general sign condition gives
\[
\operatorname{sign}(dq_L)
=
\operatorname{sign}(R_{\mathcal G,L})
=
-\operatorname{sign}(d\lambda_L),
\]
and
\[
\operatorname{sign}(dq_H)
=
-\operatorname{sign}(dq_L)
=
\operatorname{sign}(d\lambda_L).
\]
Hence, under a mean-preserving increase in \(\lambda_L\),
\[
d\lambda_L>0
\qquad\Longrightarrow\qquad
dq_L<0,
\qquad
dq_H>0,
\]
whereas
\[
d\lambda_L<0
\qquad\Longrightarrow\qquad
dq_L>0,
\qquad
dq_H<0.
\]

Thus, in the two-type case, the direction of reallocation is entirely determined by the relative proportional change in effective weights, and under a mean-preserving perturbation this reduces to the fact that \(R_{\mathcal G,H}=0\) while \(R_{\mathcal G,L}\) moves in the opposite direction from \(d\lambda_L\).

In the two-type specification,
\[
\tilde\lambda=p\lambda_L+(1-p)\lambda_H,
\qquad
\Gamma_H=\tilde\lambda\theta_H,
\qquad
\Gamma_L=\tilde\lambda J_L+\Lambda_L,
\qquad
\Lambda_L=\frac{1-p}{p}\left(\theta_H-\theta_L\right)\lambda_H.
\]
A direct computation gives
\[
R_{\mathcal G,L}-R_{\mathcal G,H}
=
\frac{(1-p)(\theta_H-\theta_L)}{\tilde\lambda\,\Gamma_L}
\left(\lambda_L\,d\lambda_H-\lambda_H\,d\lambda_L\right).
\]
Since the prefactor is positive,
\[
\operatorname{sign}(dq_L)
=
\operatorname{sign}\left(\lambda_L\,d\lambda_H-\lambda_H\,d\lambda_L\right).
\]
Equivalently, because weights are positive,
\[
\operatorname{sign}(dq_L)
=
\operatorname{sign}\left(d\left(\frac{\lambda_H}{\lambda_L}\right)\right)
=
-\operatorname{sign}\left(d\left(\frac{\lambda_L}{\lambda_H}\right)\right).
\]

So the interpretation is very sharp: what matters is not the level change in \(\lambda_L\) or \(\lambda_H\) separately, but the change in their relative ratio. Type \(L\) receives more quantity if and only if the perturbation increases \(\lambda_H/\lambda_L\), that is, if the proportional increase in welfare weight is stronger for higher types. This is exactly the two-type version of the paper’s monotonicity condition on \(\partial_t\log\lambda(t,\theta)\): the allocation shifts toward the low type when higher types receive the larger proportional increase in welfare weight, and toward the high type when lower types receive the larger proportional increase.

The reason this is non-intuitive is that the allocation depends on the effective weights \(\Gamma_t\), not on the primitive welfare weights \(\lambda_t\). In particular, low-type quantity also affects high-type informational rents, so the marginal social value of increasing \(q_L\) is partly governed by the weight placed on higher types. That is why, in screening problems, increasing \(\lambda_L\) need not increase \(q_L\).
\section{XXXX}

For the three-type case,
\[
\Gamma_H=\tilde\lambda J_H=\tilde\lambda \theta_H,
\]
and
\[
\Gamma_M=\tilde\lambda J_M+\Lambda_M
=
\tilde\lambda\left[\theta_M-\frac{p_H}{p_M}\left(\theta_H-\theta_M\right)\right]
+
\frac{p_H}{p_M}\lambda_H\left(\theta_H-\theta_M\right).
\]

Hence
\begin{align*}
\Gamma_H-\Gamma_M
&=
\tilde\lambda\theta_H
-
\tilde\lambda\left[\theta_M-\frac{p_H}{p_M}\left(\theta_H-\theta_M\right)\right]
-
\frac{p_H}{p_M}\lambda_H\left(\theta_H-\theta_M\right) \\
&=
\tilde\lambda\left(\theta_H-\theta_M\right)
+
\frac{p_H}{p_M}\tilde\lambda\left(\theta_H-\theta_M\right)
-
\frac{p_H}{p_M}\lambda_H\left(\theta_H-\theta_M\right) \\
&=
\left(\theta_H-\theta_M\right)
\left[
\tilde\lambda+\frac{p_H}{p_M}\left(\tilde\lambda-\lambda_H\right)
\right] \\
&=
\left(\theta_H-\theta_M\right)
\left[
\frac{1-p_L}{p_M}\tilde\lambda-\frac{p_H}{p_M}\lambda_H
\right].
\end{align*}

Now use
\[
\tilde\lambda=p_L\lambda_L+p_M\lambda_M+p_H\lambda_H,
\]
so
\begin{align*}
\frac{1-p_L}{p_M}\tilde\lambda-\frac{p_H}{p_M}\lambda_H
&=
\frac{1}{p_M}\left[(1-p_L)\tilde\lambda-p_H\lambda_H\right] \\
&=
\frac{1}{p_M}\left[p_M\lambda_M+p_L\lambda_L-p_L\tilde\lambda\right] \\
&=
\lambda_M-\frac{p_L}{p_M}\left(\tilde\lambda-\lambda_L\right).
\end{align*}

Therefore
\[
\Gamma_H-\Gamma_M
=
\left(\theta_H-\theta_M\right)
\left[
\lambda_M-\frac{p_L}{p_M}\left(\tilde\lambda-\lambda_L\right)
\right].
\]

For the effective weights under \(\beta>0\), write
\[
\mathcal G_H-\mathcal G_M
=
\left(\Gamma_H-\Gamma_M\right)+\beta\left(J_H-J_M\right).
\]
Using
\[
J_H-J_M
=
\theta_H-\left[\theta_M-\frac{p_H}{p_M}\left(\theta_H-\theta_M\right)\right]
=
\frac{1-p_L}{p_M}\left(\theta_H-\theta_M\right),
\]
we obtain
\[
\mathcal G_H-\mathcal G_M
=
\left(\theta_H-\theta_M\right)
\left[
\lambda_M-\frac{p_L}{p_M}\left(\tilde\lambda-\lambda_L\right)
+
\beta\frac{1-p_L}{p_M}
\right].
\]

Under the normalization
\[
p_L=p_M=p_H=\frac13,\qquad \theta_H=1,\qquad \theta_M=\theta_L+d,
\]
this becomes
\[
\mathcal G_H-\mathcal G_M
=
\left(1-\theta_L-d\right)
\left[
\lambda_M-\left(\tilde\lambda-\lambda_L\right)+2\beta
\right].
\]

For the three-type case,
\[
\Gamma_M=\tilde\lambda J_M+\Lambda_M
=
\tilde\lambda\left[\theta_M-\frac{p_H}{p_M}\left(\theta_H-\theta_M\right)\right]
+
\frac{p_H}{p_M}\lambda_H\left(\theta_H-\theta_M\right),
\]
and
\[
\Gamma_L=\tilde\lambda J_L+\Lambda_L
=
\tilde\lambda\left[\theta_L-\frac{1-p_L}{p_L}\left(\theta_M-\theta_L\right)\right]
+
\frac{p_M\lambda_M+p_H\lambda_H}{p_L}\left(\theta_M-\theta_L\right).
\]

Hence
\begin{align*}
\Gamma_M-\Gamma_L
&=
\tilde\lambda\left[\theta_M-\frac{p_H}{p_M}\left(\theta_H-\theta_M\right)\right]
+
\frac{p_H}{p_M}\lambda_H\left(\theta_H-\theta_M\right) \\
&\qquad
-
\tilde\lambda\left[\theta_L-\frac{1-p_L}{p_L}\left(\theta_M-\theta_L\right)\right]
-
\frac{p_M\lambda_M+p_H\lambda_H}{p_L}\left(\theta_M-\theta_L\right) \\
&=
\tilde\lambda\left(\theta_M-\theta_L\right)
-
\frac{p_H}{p_M}\tilde\lambda\left(\theta_H-\theta_M\right)
+
\frac{1-p_L}{p_L}\tilde\lambda\left(\theta_M-\theta_L\right) \\
&\qquad
+
\frac{p_H}{p_M}\lambda_H\left(\theta_H-\theta_M\right)
-
\frac{p_M\lambda_M+p_H\lambda_H}{p_L}\left(\theta_M-\theta_L\right).
\end{align*}

Collecting the \(\left(\theta_M-\theta_L\right)\) terms and the \(\left(\theta_H-\theta_M\right)\) terms gives
\begin{align*}
\Gamma_M-\Gamma_L
&=
\left(\theta_M-\theta_L\right)
\left[
\tilde\lambda+\frac{1-p_L}{p_L}\tilde\lambda
-
\frac{p_M\lambda_M+p_H\lambda_H}{p_L}
\right] \\
&\qquad
+
\left(\theta_H-\theta_M\right)
\left[
\frac{p_H}{p_M}\lambda_H-\frac{p_H}{p_M}\tilde\lambda
\right].
\end{align*}

Now simplify each bracket separately. For the first bracket,
\begin{align*}
\tilde\lambda+\frac{1-p_L}{p_L}\tilde\lambda
-
\frac{p_M\lambda_M+p_H\lambda_H}{p_L}
&=
\frac{1}{p_L}\tilde\lambda
-
\frac{p_M\lambda_M+p_H\lambda_H}{p_L} \\
&=
\frac{\tilde\lambda-p_M\lambda_M-p_H\lambda_H}{p_L} \\
&=
\frac{p_L\lambda_L}{p_L} \\
&=
\lambda_L.
\end{align*}

For the second bracket,
\begin{align*}
\frac{p_H}{p_M}\lambda_H-\frac{p_H}{p_M}\tilde\lambda
&=
\frac{p_H}{p_M}\left(\lambda_H-\tilde\lambda\right).
\end{align*}

Therefore
\[
\Gamma_M-\Gamma_L
=
\lambda_L\left(\theta_M-\theta_L\right)
+
\frac{p_H}{p_M}\left(\lambda_H-\tilde\lambda\right)\left(\theta_H-\theta_M\right).
\]

For the effective weights under \(\beta>0\), write
\[
\mathcal G_M-\mathcal G_L
=
\left(\Gamma_M-\Gamma_L\right)+\beta\left(J_M-J_L\right).
\]
Using
\begin{align*}
J_M-J_L
&=
\left[\theta_M-\frac{p_H}{p_M}\left(\theta_H-\theta_M\right)\right]
-
\left[\theta_L-\frac{1-p_L}{p_L}\left(\theta_M-\theta_L\right)\right] \\
&=
\left(\theta_M-\theta_L\right)
+
\frac{1-p_L}{p_L}\left(\theta_M-\theta_L\right)
-
\frac{p_H}{p_M}\left(\theta_H-\theta_M\right) \\
&=
\frac{\theta_M-\theta_L}{p_L}
-
\frac{p_H}{p_M}\left(\theta_H-\theta_M\right),
\end{align*}
we obtain
\[
\mathcal G_M-\mathcal G_L
=
\lambda_L\left(\theta_M-\theta_L\right)
+
\frac{p_H}{p_M}\left(\lambda_H-\tilde\lambda\right)\left(\theta_H-\theta_M\right)
+
\beta\left[
\frac{\theta_M-\theta_L}{p_L}
-
\frac{p_H}{p_M}\left(\theta_H-\theta_M\right)
\right].
\]

Under the normalization
\[
p_L=p_M=p_H=\frac13,\qquad \theta_H=1,\qquad \theta_M=\theta_L+d,
\]
this becomes
\[
\mathcal G_M-\mathcal G_L
=
\lambda_L d
+
\left(\lambda_H-\tilde\lambda\right)\left(1-\theta_L-d\right)
+
\beta\left(\theta_L+4d-1\right).
\]


\section{XXXX}
Let
\[
F(\theta_L,\lambda_L)
:=
\theta_L \;p\frac{R_q(q_L)}{\Gamma_L}
+ \theta_H  \; (1-p)\frac{R_q(q_H)}{\Gamma_H}
- (\theta_H-\theta_L) \; (1 - p)\frac{R_q(q_L)}{\Gamma_L}.
\]
The cutoff \(\lambda_L\) is defined implicitly by
\[
F(\theta_L,\lambda_L)=0.
\]

To understand the sign of \(\frac{d\lambda_L}{d\theta_L}\), it is useful to first study the effect of \(\theta_L\) on \(F\). Holding fixed \(R_q\) and \(\Gamma_H\), differentiating with respect to \(\theta_L\) gives
\begin{align*}
\frac{\partial F}{\partial \theta_L}
&=
p\frac{R_q(q_L)}{\Gamma_L}
+
(1-p)\frac{R_q(q_L)}{\Gamma_L}
-
\left[\theta_L-(1-p)\theta_H\right]
\frac{R_q(q_L)}{\Gamma_L^2}
\frac{\partial \Gamma_L}{\partial \theta_L} \\
&=
\frac{R_q(q_L)}{\Gamma_L}
-
\left[\theta_L-(1-p)\theta_H\right]
\frac{R_q(q_L)}{\Gamma_L^2}
\frac{\partial \Gamma_L}{\partial \theta_L}.
\end{align*}

This expression admits a natural economic decomposition.

The first term,
\[
\frac{R_q(q_L)}{\Gamma_L}>0,
\]
is the direct positive effect of increasing \(\theta_L\). It combines two forces:

\begin{itemize}
    \item a surplus effect: a higher \(\theta_L\) raises the first term
    \[
    \theta_L p \frac{R_q(q_L)}{\Gamma_L},
    \]
    so more surplus can be redistributed;

    \item an incentive effect: a higher \(\theta_L\) reduces the information gap
    \[
    \theta_H-\theta_L,
    \]
    and therefore lowers the IC-rent term
    \[
    (\theta_H-\theta_L)(1-p)\frac{R_q(q_L)}{\Gamma_L}.
    \]
\end{itemize}

Hence, absent any change in \(\Gamma_L\), increasing \(\theta_L\) has an unambiguously positive effect on \(F\).

The second term,
\[
-
\left[\theta_L-(1-p)\theta_H\right]
\frac{R_q(q_L)}{\Gamma_L^2}
\frac{\partial \Gamma_L}{\partial \theta_L},
\]
is the cost of increasing \(\Gamma_L\). Since \(\Gamma_L\) appears in the denominator, a rise in \(\Gamma_L\) lowers the return
\[
\frac{R_q(q_L)}{\Gamma_L}.
\]
Thus, even though increasing \(\theta_L\) has a direct positive effect, part of that gain is offset because it also raises the effective weight \(\Gamma_L\).

The sign of \(\frac{\partial F}{\partial \theta_L}\) therefore reflects a trade-off:
\[
\text{net positive effect of higher } \theta_L
\quad
\text{versus}
\quad
\text{cost of the induced increase in } \Gamma_L.
\]

In the two-type case, this trade-off can be resolved explicitly. Using
\[
\Gamma_{L,\theta_L}=\lambda_L,
\]
one gets
\[
\frac{\partial F}{\partial \theta_L}
=
\frac{R_q(q_L)}{\Gamma_L^2}
\left[
\Gamma_L-\left(\theta_L-(1-p)\theta_H\right)\lambda_L
\right],
\]
and the bracket simplifies to
\[
\Gamma_L-\left(\theta_L-(1-p)\theta_H\right)\lambda_L
=
(1-p)\lambda_H\theta_H>0.
\]
Hence
\[
\frac{\partial F}{\partial \theta_L}>0.
\]

So the direct positive effect of increasing \(\theta_L\) dominates the denominator cost coming from the increase in \(\Gamma_L\).

Starting from
\[
F(\theta_L,\lambda_L)
=
\theta_L \;p\frac{R_q(q_L)}{\Gamma_L}
+ \theta_H  \; (1-p)\frac{R_q(q_H)}{\Gamma_H}
- (\theta_H-\theta_L) \; (1 - p)\frac{R_q(q_L)}{\Gamma_L},
\]
and holding fixed \(R_q\) and \(\Gamma_H\), differentiating with respect to \(\lambda_L\) gives
\begin{align*}
\frac{\partial F}{\partial \lambda_L}
&=
-\theta_L p \frac{R_q(q_L)}{\Gamma_L^2}\frac{\partial \Gamma_L}{\partial \lambda_L}
+
(\theta_H-\theta_L)(1-p)\frac{R_q(q_L)}{\Gamma_L^2}\frac{\partial \Gamma_L}{\partial \lambda_L} \\
&=
-\left[\theta_L p-(\theta_H-\theta_L)(1-p)\right]
\frac{R_q(q_L)}{\Gamma_L^2}\frac{\partial \Gamma_L}{\partial \lambda_L} \\
&=
-\left[\theta_L-(1-p)\theta_H\right]
\frac{R_q(q_L)}{\Gamma_L^2}\frac{\partial \Gamma_L}{\partial \lambda_L}.
\end{align*}

This expression admits the following economic interpretation.

An increase in \(\lambda_L\) raises the effective return weight \(\Gamma_L\). Since \(\Gamma_L\) appears in the denominator, this lowers the return
\[
\frac{R_q(q_L)}{\Gamma_L}.
\]
This has two opposite consequences:

\begin{itemize}
    \item it reduces the first term
    \[
    \theta_L p\frac{R_q(q_L)}{\Gamma_L},
    \]
    which lowers \(F\);

    \item it also reduces the magnitude of the IC-rent term
    \[
    (\theta_H-\theta_L)(1-p)\frac{R_q(q_L)}{\Gamma_L},
    \]
    which raises \(F\), since this term enters with a minus sign.
\end{itemize}

Hence, at this stage, the effect of \(\lambda_L\) is the net result of

\[
\text{a negative compression of the direct surplus term}
\quad\text{versus}\quad
\text{a positive compression of the IC-rent term}.
\]

In the two-type case, this ambiguity can be resolved explicitly. Using
\[
\Gamma_{L,\lambda_L}
=
\theta_L-(1-p)\theta_H,
\]
we obtain
\[
\frac{\partial F}{\partial \lambda_L}
=
-\left[\theta_L-(1-p)\theta_H\right]^2
\frac{R_q(q_L)}{\Gamma_L^2}.
\]
Therefore,
\[
\boxed{
\frac{\partial F}{\partial \lambda_L}<0.
}
\]

So in the two-type case, the negative effect dominates: increasing \(\lambda_L\) raises \(\Gamma_L\), which compresses the low-type return \(\frac{R_q(q_L)}{\Gamma_L}\) enough to reduce \(F\) overall.
\end{document}
