\documentclass{class}

\definecolor{ok}{RGB}{0,140,0}
\definecolor{todo}{RGB}{180,0,0}
\newcommand{\ok}{\textcolor{ok}{\textbf{[RESOLVED]}}}
\newcommand{\todo}{\textcolor{todo}{\textbf{[OPEN]}}}

\title{Notation Audit Log --- Redistributive Peak Load Pricing}
\author{Pass A, Pass B, Pass C, Pass D}
\date{}

\begin{document}
\maketitle

\section*{Pass A --- Notation and Placeholder Audit (Round 1)}

\begin{enumerate}[leftmargin=1.5cm]
\item \ok\ $\Lambda_i(\theta)$: subscript $i$ missing from conditional expectation operator.
\item \ok\ $\mathbb{E}\underline{CS}_i$ used as decision variable vs.\ endogenous object; replaced by $\mathbb{E}\underline{CS}_i$ throughout (kept as is after discussion).
\item \ok\ $k_i$, $I_i$ undefined in Section 3.1; resolved by verbal introduction as category-specific parameters.
\item \ok\ $\partial_k$ vs.\ $d_k$ notation inconsistency in two-type section; fixed to $\partial_k$ throughout.
\item \ok\ $\mathbb{E}_i^w[\cdot\mid s]$ used before general definition; definition sentence added inline.
\item \ok\ $R_{\mathcal{G},i}(\theta)$ vs.\ $R_\mathcal{G}(\theta)$: deliberate readability choice, accepted.
\item \ok\ $R_{\theta,i}(\theta)$ vs.\ $R_\theta(\theta)$: same as above, accepted.
\item \ok\ Roman $ECS(\theta_L)$ vs.\ $\mathbb{E}CS_i(\theta)$; fixed to $\mathbb{E}CS(\theta_L)$ in two-type section.
\item \ok\ Missing backslash before E in (ECS$_i^\times$) underbrace; fixed.
\item \ok\ ``As shown in Proposition~\ref{lem:investment}'' should be ``Lemma''; fixed.
\item \ok\ Sentence ending ``which yields.'' with no completion; fixed.
\item \ok\ $\mathbb{E}_{(s,i)}^w\mathrm{Var}[uJ]$ inconsistent with $\mathbb{E}_{(s,i)}^w[\mathrm{Var}_i(uJ)]$; fixed.
\item \ok\ $\Delta_\lambda\beta_i$ undefined in main text; reference to proof added.
\item \ok\ Missing $\partial$ in denominator of \eqref{eq:proof-dECSbar-dbeta}; fixed.
\item \ok\ $\varepsilon_i(s)$ incorrectly said to be multiplier on \eqref{K-def} instead of \eqref{Kmdi-def}; fixed.
\item \ok\ Underbrace labels in Proposition 2 CARA reduction: deliberate presentational choice, accepted.
\end{enumerate}

\section*{Pass B --- Notation and Placeholder Audit (Round 2)}

\begin{enumerate}[leftmargin=1.5cm]
\item \ok\ $\mathbb{E}_{(s,i)}[\cdot]$ used before definition in constraint (R); definition sentence added after the constraint.
\item \ok\ $\tilde\lambda_i I_i$ inside expectation in (CS): deliberate, accepted.
\item \ok\ Step 1 of Theorem proof referenced \eqref{ECSi} instead of \eqref{partialkCS1}; fixed to \eqref{partialkCS1}.
\item \ok\ $\mathbb{E}CS(\theta_L)$ without category subscript in two-type section; deliberate (section declares $i\in\{L,H\}$), accepted.
\item \ok\ $i,j$ used as type indices in $dq_i/R_q(\theta_i)=dq_j/R_q(\theta_j)$; deliberate, accepted.
\item \ok\ $\Gamma_L/\Gamma_H$ vs.\ $\mathcal{G}_L/\mathcal{G}_H$ in two-type section; deliberate under $\beta=0$, accepted.
\item \ok\ Local $\mathrm{Var}_i$ in Appendix A.1.2 conflicts with general $\mathbb{E}_{(s,i)}^w[\mathrm{Var}_i(uJ)]$; accepted (local notation only).
\item \ok\ $\Omega_i$ undefined at first use in proof of Theorem~\ref{thm:surplus} Step 2. \textbf{Fix:} add ``where $\Omega_i:=\mathbb{E}_s[1/\overline{w}_i(s)\,\mathbf{1}_{\{s\in T_i\}}]$, as defined in Lemma~\ref{lem:dkidk}'' at start of Step 2.
\item \ok\ Mixed Leibniz and subscript notation for second derivatives in Lemma~\ref{lem:Vi-concave} Step 3; fixed.
\item \ok\ Cross-reference labels \eqref{eq:proof-Vi-Iderivs}--\eqref{eq:proof-Vi-kk} inside nested proof environments; accepted.
\item \ok\ $\theta$ vs.\ $\theta^\ast(q,s)$ in ($\Delta_1 p_i$): offending paragraph deleted.
\item \ok\ $\tilde\lambda^\ast$ used before its definition in Lemma~\ref{lem:investment}; fixed.
\item \ok\ $R^M(k)$ in proof of Proposition~\ref{prop:CI-surplus} never defined. \textbf{Fix:} define $R^M(k):=\mathbb{E}_{(s,i)}[\theta U(q_i^\ast(\theta_i^\ast(k),s),s)]- I(k)/\mu^c$ or replace with verbal statement.
\item \ok\ Local redefinition of $\mathbb{E}_{(s,i)}^w[uJ\mid s]$ in Lemma~\ref{lem:Vi-concave} Step 2; accepted (equivalent expression).
\item \ok\ $M(k)$ in ``$B(k)+M(k)\neq 0$'' in proof of Proposition~\ref{prop:CI-surplus} never defined. \textbf{Fix:} define $M(k)$ explicitly as the inframarginal term or absorb it into $B(k)$.
\end{enumerate}

\section*{Pass B --- Notation and Placeholder Audit (Round 3)}

\begin{enumerate}[leftmargin=1.5cm]
\item \ok\ Spurious double backslash \texttt{\\\\E} before the expectation operator in the definition sentence after constraint (R); fixed to single \texttt{\\E} throughout.
\item \ok\ $\Delta\tilde\lambda_i$ undefined in the display for $\Delta\G_i(\theta)$. \textbf{Fix:} added $\Delta\tilde\lambda_i = \E_i[\Delta\lambda_i(\theta)]$ inline after the definition of $\Delta\Lambda_i(\theta)$.
\item \ok\ $\E_i^w[\cdot\mid s]$ vs.\ $\mathbb{E}_i^w[\cdot\mid s]$: confirmed that \texttt{\\E} macro normalizes to \texttt{\\mathbb\{E\}} throughout; all occurrences are identical on output.
\item \ok\ Assumption~\ref{ass:Cvx} not referenced in Lemma~\ref{lem:FOC} statement: closed by author decision, convexity condition stated verbally in the lemma.
\item \ok\ $\mathbb{E}_s[\cdot]$ vs.\ $\E_s[\cdot]$ in equation (EuJ): fixed by normalizing to \texttt{\\E} macro throughout.
\item \ok\ $\bar\varepsilon_i$ (\texttt{\\bar}) vs.\ $\overline\varepsilon_i$ (\texttt{\\overline}) in proof of Proposition~\ref{prop:revenueordering} CARA Steps 1--3: fixed to $\overline\varepsilon_i$ throughout.
\item \ok\ $T_{i0}$ undefined in proof of Lemma~\ref{lem:Transfer}: renamed to $\underline{t}_i$, defined as the transfer to the lowest type $\underline\theta_i$, avoiding conflict with on-peak set $T_i$.
\item \ok\ Malformed double opening parentheses in three-type condition in Appendix~A.1.2: fixed throughout the expression.
\item \ok\ $\mathrm{Cov}_i$ vs.\ $\Cov_i$ and $\mathrm{Var}_i$ vs.\ $\Var_i$: normalized to a single macro throughout.
\item \ok\ $\beta_i^\Delta+\tilde\lambda_i^\Delta=\beta_i+\tilde\lambda_i$ attributed to proof of Proposition~\ref{prop:surplus-redist}: misattribution confirmed; condition appears only in proof of Proposition~\ref{prop:rprefreallocation} and follows from the IR-constrained definition at both baseline and perturbed optimum in Proposition~\ref{prop:surplus-redist}. No fix required.
\item \ok\ $\Delta k$ and $\Delta I$ undefined in ($\Delta_2 p_i$): fixed by adding sentence ``where $\Delta k := k_j^\ast - k_i^\ast$ and $\Delta I := I_j^\ast - I_i^\ast$ denote the differences in equilibrium capacity and revenue requirement between the two adjacent categories $i$ and $j$'' before the equation.
\item \ok\ $\E_\theta[\cdot]$ in Assumption~\ref{ass:ordered-path} inconsistent with $\E_i[\cdot]$ convention: fixed by replacing with explicit integral $\tilde\lambda(t):=\int_\Theta\lambda(t,\theta)\,dG(\theta)$.
\item \ok\ $\E_i[R_\theta^2(\theta)]$ typographically ambiguous and inconsistent with $\E_i[R_\theta^2]$ in Step 2 of the same proof: fixed to $\E_i[(R_\theta(\theta))^2]$ throughout.
\end{enumerate}

\section*{Pass C --- Notation and Placeholder Audit (Conversation Round 1)}

\begin{enumerate}[leftmargin=1.5cm]
\item \ok\ Abstract placeholders ``200 words'' and ``100 words'' identified; closed by author decision / removed in final clean version.
\item \ok\ Footnote invoking Assumption Int before its formal statement; closed by author decision.
\item \ok\ $R_q(\theta)$ defined as a function of $\theta$ while depending on $s$ through $q_i(\theta,s)$; accepted as a readability convention.
\item \ok\ Equation (EuJ) drops explicit dependence on $k_i$; accepted as a readability convention after noting boundary effects are null.
\item \ok\ Assumption CARA originally written as marginal utility using $U$ notation; corrected to
\[
U(q,s)=\frac{v(s)}{\alpha}\left(1-e^{-\alpha q}\right),
\qquad
u(q,s)=v(s)e^{-\alpha q}.
\]
\item \ok\ Duplicate tag \((ECSLH)\) in the two-type illustration; closed by author decision.
\item \ok\ Scalar $w$ in the two-type correspondence not separately defined from $w_i(\theta,s)$ and $w_i(s)$; accepted as the two-type analogue.
\item \ok\ Text referring to ``change of available surplus \(EuJ\)'' potentially conflating \(ECS_i\) and the capacity-sorting object; closed.
\item \ok\ Contributor/non-contributor wording around slack budget constraints in Proposition 2 discussion; closed by author decision.
\item \ok\ Display tagged \((d\lambda^\ast)\) and subsequent text using $d\lambda^\ast$ rather than $d\tilde\lambda^\ast$; accepted as an equation label / closed.
\item \ok\ Nonlinear tariff numerical description: sign of the welfare-weight slope \(a_i\) checked for consistency with the stated direction of favored types; fixed where needed.
\item \ok\ Appendix A.2 unmatched parentheses in the two-type and three-type allocation-incidence formulas; fixed.
\item \ok\ Definition 1 missing explicit second variable in log-submodularity/log-supermodularity wording; fixed or accepted after clarifying the cross-partial is in \((\theta,k_i)\).
\item \ok\ Footnote on utilitarian designer corrected so that \(\lambda_i(\theta)=1\), not \(G_i(\theta)\).
\item \ok\ Proof of Lemma 4 feasible set corrected to use population-weighted aggregate constraints consistently with the outer problem.
\item \ok\ Proof of Theorem 2 stray \(\theta^\ast\) in \(E_i[R_G(\theta^\ast)]\); fixed to the intended type-average expression.
\item \ok\ Lemma 5 assumptions on uniqueness/interiority/strict convexity/Inada conditions; closed by author decision because the relevant conditions are maintained in the environment.
\end{enumerate}

\section*{Pass D --- Notation and Placeholder Audit (Conversation Round 2)}

\begin{enumerate}[leftmargin=1.5cm]
\item \ok\ Footnote 17: \(\Lambda_i^1\), \(\Lambda_i^2\), and \(\Lambda_i^\Delta\) used before being formally introduced; fixed by aligning notation with Lemma 7.
\item \ok\ Assumption CARA: environment assumes \(u_s>0\); CARA statement updated to include \(v_s(s)>0\).
\item \ok\ Proof of Lemma 2: references to parts (i) and (ii) removed or aligned with the lemma statement.
\item \ok\ Proof of Theorem 2: capacity multiplier notation \(\mu_k\) replaced by \(\zeta_k\).
\item \ok\ Lemma 10: positivity condition used in proof clarified or closed under maintained support assumptions.
\item \ok\ Proof of Corollary 1: revenue multiplier notation \(\mu_I\) replaced by \(\zeta_I\).
\item \ok\ Proof of Corollary 1: reference to ``This proves (iii)'' removed or aligned with the corollary statement.
\item \ok\ Definition 1: log-submodularity wording corrected from ``in \((\theta)\)'' to ``in \((\theta,k_i)\)''.
\item \ok\ Section 6 discussion after \((\Delta_3 p_i)\): category-specific preference direction and welfare-weight slope signs corrected.
\item \ok\ Section 6 discussion after \((\Delta_3 p_i)\): statement about lower types being favored by welfare weights aligned with the stated numerical parameters.
\end{enumerate}

\section*{Pass E --- Notation and Placeholder Audit (Conversation Round 3)}

\begin{enumerate}[leftmargin=1.5cm]
\item \ok\ Lemma 1 transformed budget constraint tag \((R)\) reused original revenue-constraint tag; fixed by distinguishing \((R^\times)\) and transformed \((R)\), or by author-approved convention.
\item \ok\ Section 3.1 available-surplus constraint tag \((ECS_i)\) reused envelope tag; fixed by distinguishing \((ECS_i^\times)\) and \((ECS_i)\).
\item \ok\ Section 3.1 single-category objective tag \((CS)\) reused transformed objective tag; fixed by distinguishing \((CS^\times)\) and \((CS)\).
\item \ok\ Footnote referencing ``part (ii)'' of Theorem 1; removed or rewritten because Theorem 1 is not formally numbered into parts.
\item \ok\ Section 3.5: individual surplus change denoted both \(\Delta CS_i(\theta)\) and \(\Delta ECS_i(\theta)\); normalized to \(\Delta ECS_i(\theta)\).
\item \ok\ Proposition 2 discussion: \(\tilde\lambda^\ast\) used before formal definition in Lemma 5; fixed by defining the common shadow value earlier or by adding a local definition.
\item \ok\ Proposition 2 extensive-margin statement: empty-set convention for \(\max_{i\in N^+}\) and \(\min_{i\in N^0}\) clarified or closed by author decision.
\item \ok\ Lemma 5: division by \(\mu^+\) clarified by assuming \(N^+\neq\varnothing\) or \(\mu^+>0\) where needed.
\item \ok\ Figure 7 numerical description: \(\tilde\lambda_2=-1.1\) corrected to \(\tilde\lambda_2=1.1\).
\item \ok\ Figure 7 numerical description: nonnegativity of welfare weights restored by correcting the average weight sign.
\item \ok\ Proof of Lemma 4: outer objective corrected from \(W:=\sum_i V_i\) to \(W:=\sum_i\mu_i V_i\).
\item \ok\ Proposition 5: additional restriction used in the proof of part (ii) either added to the statement or closed by author decision.
\item \ok\ Lemma 8: positivity of \(B\) under \(I''(k^\ast)>0\) clarified or closed under maintained strict convexity of \(I\).
\end{enumerate}

\section*{Pass F --- Notation and Placeholder Audit (Conversation Round 4)}

\begin{enumerate}[leftmargin=1.5cm]
\item \ok\ Section 3.5 display before Proposition 1: individual surplus-change equation written as \(\Delta ECS_i=\Delta ECS_i+\int_{\underline\theta_i}^{\theta}\cdots\); fixed to use the type-dependent object \(\Delta ECS_i(\theta)\) on the left-hand side.
\item \ok\ Appendix A.5, Lemma 7: statement gave both \(\geq\) and ``resp. \(\leq\)'' cases after assuming only that \(m_i(\theta)\) is increasing; fixed by explicitly adding the decreasing case.
\item \ok\ Appendix C.1, proof of Lemma 1: scalar \(t_i\) introduced as the transfer of the lowest type while \(t_i(\theta,s)\) denotes the transfer schedule; fixed by defining a distinct scalar transfer for the lowest type, e.g.\ \(\underline t_i\).
\end{enumerate}

\section*{Summary of Open Items}

None.

\end{document}